Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-04-02 paper.tex
update

\begin{document}
\maketitle
\vspace{-0.8cm}
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of quality requirements. Therefore, we propose a comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable balance on both sides. Further, we develop a PSO-based service composition approach with explicit support for the comprehensive model. We also conduct experiments to address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model.

@@

\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composite service that accommodates customers' complex requirements. 
%This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. 
Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies, such as $WSDL$, $SOAP$. The semantic dimension enables a better collaboration through ontology-based semantics, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. Another challenge is related to QoS optimisation. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.

@@

The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model. We will achieve three objectives in this work:

@@

 \item To propose a PSO-based service composition approach using the proposed comprehensive quality model. To do that, we aim to find a service candidate queue that can be decoded into a service composition with near-optimal comprehensive quality.  
 \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
\end{enumerate}
\vspace{-0.5cm}
\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic descriptions of web services' parameters using some kind of logic (e.g., description logic) that ensures the interoperability of web services. In these approach, the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions. However, this evaluation approach does not guarantee an optimised QoS of composition solutions.

QoS-aware web service composition is studied using traditional approaches or EC techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a local optimisation and enumeration method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are widely used to automatically generate solutions with optimal QoS. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Yu et al.  \cite{yu2013adaptive} use GP for finding near-optimal solutions that are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based representations, which are transformed from graph-based representations. To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where graph-based evolutionary operators are employed. An indirect PSO-based approach was introduced in \cite{da2016particle}. An service queue is used as an indirect representation that is decoded into a \emph{directed acyclic graph} (DAG). These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only evaluated with some simple cases.

@@

\section{Motivation and Problem Description}\label{Motivation and Problem Description}\label{Motivation}\label{problemDes}\label{qualityModel}\label{Comprehensive_Quality_Model}\label{qualityModel}

@@

We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$. The inputs in $I_{S}$ and the outputs in $O_{S}$ are concept-related parameters with the concepts in an ontology $\mathcal{O}$. The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively. These four QoS attributes are most commonly used \cite{zeng2003quality}.
% \textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received. \textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service. \textit{Reliability} ($r_S$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0. Similarly, \textit{availability} ($a_S$) is the probability that a service is accessible.

A \emph{service repository} $\mathcal{SR}$ is a finite collection of services with a common ontology $\mathcal{O}$. A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs. The inputs in $I_{T}$ and the outputs in $O_{T}$ are concept-related parameters with the concepts in the ontology $\mathcal{O}$.

A service composition is commonly represented as a DAG. It nodes correspond to the services in the composition. Two services $S$ and $S'$ are connected by an edge $e$ if some output of $S$ serves as input for $S'$. Apparently, such outputs and inputs must semantically match to ensure the correct execution of the service composition. 
%Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
%To answer a request from a user a suitable service composition is sought. 
The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services. The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ is a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
%($a \perp b$)
In this paper we are only interested in robust compositions where only $exact$ and $plugin$ matches are considered, see \cite{lecue2009optimizing}. 
%
As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing. We suggest to consider the semantic similarity of concepts when comparing different plugin types. For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively. 
\vspace{-0.2cm}

@@

\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see \ref{PSO_based_approach}. However, if more than one pair of matched output and input exist from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.

@@

%\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Formula (\ref{equation2}).

@@

%Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge. Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in formula (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.

@@

%Consequently, in Formula \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
\vspace{-0.1cm}
\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is proposed as a \emph{comprehensive quality model}, which can be defined as a weighted sum of the individual criteria: 
\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{SIM} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent with $\sum_{k=1}^{6} w_k= 1$. The weights can be adjusted according to users' preferences. Herein, the individual criteria are normalised to a range between 0 to 1, where 1 means the best value and 0 means the worst. For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}). To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$. $MT$ and $S$ have minimum value 0 and maximum value 1. The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see \ref{PSO_based_approach}.

@@

\noindent The composition task is to find the maximum value of objective function in (\ref{equation8}).

@@

\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
\vspace{-0.8cm}
\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{An overview of POS-based approach to comprehensive quality-aware automated semantic web service composition.}
 \label{overview}
\end{figure}
\vspace{-1.0cm}
\subsection{An Overview to PSO-based Method}\label{PSO_based_approach}

@@

Step 1: The composition process is triggered by a composition task, which is clearly defined in \ref{problemDes}.

Step 2: This composition task is used to discover all task-related service candidates using a greedy search algorithm adopted from \cite{ma2015hybrid}, which contributes to a shrunken service repository. This greedy search algorithm keeps adding outputs of the invoked services as available outputs (initialised with $I_{T}$) , and these available outputs are used to discover task-related services from a service repository and updated with the outputs of these discovered services. This operation is repeated until no service is satisfied by the available outputs. During the greedy search, an ontology-based cache ($cache$) is initialised, which stores the concept similarities of matched inputs and outputs of task-related candidates. This $cache$ is also used to discover services by checking whether $null$ is returned by given two output-related and input-related concepts.

Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes. In particular, these two differences are related to sorting a created service queue using service-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively. Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.

\subsection{PSO-based Approach Algorithm}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and creating a WG from service queue (Algorithm \ref{graph_building}). In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position. Each service candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0. In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order. In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$. In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
\vspace{-0.5cm}
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Create a service candidates queue and map service candidates to a particle's position vectors\;
     Sort the service queue by position vectors' weights\;
     Create a $WG$ from the service queue (Algorithm\ref{graph_building}) \;
     Calculate the $WG$ fitness value\;

@@

\vspace{-0.5cm}
Algorithm  \ref{graph_building} is a forward graph building algorithm extended from \cite{blum1997fast}. This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}. Note that different service queues may lead to different $WGs$. In addition. $I_{T}$, $O_{T}$ and $cache$ are also taken as the inputs. Firstly, $Start$ and $End$ are added to $V$ of $WG$ as an initialisation, and $OutputSet$ is also created with $I_{T}$. The following steps are repeated until $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$. If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$. Otherwise, the second popped  $S$ from $queue$ is considered for these operations. Meanwhile, $e$ is created with $type_e$ and $sim_e$ if $S$ is added, and calculated using information provided from $cache$. This forward graph building technique could lead to more services and edges connected to the $WG$, these redundancies should be removed before $WG$ is returned.
\vspace{-0.5cm}

\begin{algorithm}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{createWeightedDAG}{createWeightedDAG}
 \SetKwProg{Procedure}{Procedure}{}{}
 %\LinesNumbered
 \SetNlSty{}{}{:}
 % \Procedure{}{
 \Input{ $I_T$, $O_T$, $queue$, $cache$}
 \Output{WG}
 $WG = (V, E)$\;
 $V \leftarrow$ \{$Start$, $End$ \} \;
 $OutputSet \leftarrow$ \{$I_{T}$\}\;
  \While { $O_{T}$ do not satisfied by $OutputSet$}{
     \ForEach{$S$ in $queue$}{
      \uIf{all $I_{S}$ satisfied by $OutputSet$}{  
        $V$ add $S$\;  
        $OutputSet$ add \{$O_{S}$\}\;
        $queue$.remove $S$\;   
        $e \leftarrow$ calculate $type_e$, $sim_e$ using $cache$\;
        $E$ add $e$\;
       }	
     }
  }
 remove $dangling$ $nodes$\; 
 remove $dangling$ $edges$\;
 \KwRet $WG$\;
 %}
 \caption{Create a $WG$ from a sorted service queue.}
\label{graph_building}
\end{algorithm}

@@

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.29]{comparisontest.pdf}}}
 \caption{An example of comparison to best solutions for QoS model and comprehensive quality evluation model using Task 3.}
 \label{comparisontest}
\end{figure}
\vspace{-1.0cm}

>>>>

\begin{document}
\maketitle
\vspace{-0.8cm}
\begin{abstract}
Web service composition has been a prevailing research direction in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, such as minimum cost and maximum reliability. To meet the requirements of service users, both semantic matchmaking quality and QoS should be considered simultaneously. Most existing works on web service composition, however, focus only on one of these two aspects. Therefore, we propose a comprehensive quality model that takes both semantic matchmaking quality and QoS into account with the aim of achieving a more desirable balance of both sides. Further, we develop a PSO-based service composition approach with explicit support for the proposed comprehensive quality model. We also conduct experiments to explore the effectiveness of our PSO-based approach and the desirable balance achieved by using our comprehensive quality model.

@@

\textit{Web service composition} aims to loosely couple a set of web services to provide a value-added composite service that accommodates complex functional and non-functional requirements of service users. 
%This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. 
Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies, such as $WSDL$, $SOAP$. The semantic dimension enables a better collaboration through ontology-based semantics, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. Another challenge is related to QoS optimisation. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.

@@

The overall goal of this paper is to \textit{develop a PSO-based approach to comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works on QoS-aware service composition by considering jointly optimising QoS and semantic matchmaking quality, which is proposed as a comprehensive quality model. We will achieve three objectives in this work:

@@

 \item To propose a PSO-based service composition approach using the proposed comprehensive quality model. To do that, we aim to find a service candidate queue that can be decoded into a service composition with near-optimal comprehensive quality.  
 \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
\end{enumerate}
\vspace{-0.5cm}
\section{Related Work} \label{relatedWork}
While web service composition has attracted much research over the last decade, most efforts focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, Only very few works address both semantic matchmaking quality and QoS for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported about first attempts that consider both aspects together.

Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures semantic descriptions of the parameters of web services using some kind of logic (i.e., description logic) to ensure the interoperability of web services. In these approaches, the goal is often to minimise the number of services or the size of a graph representation for a web service composition to obtain optimised composition solutions. However, these approaches do not guarantee an optimised QoS of service compositions.

QoS-aware web service composition, on the other side, has been studied using classical optimisation techniques or EC techniques for finding near-optimised solutions. \cite{qi2010combining} proposes a local optimisation and enumeration method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are widely used to automatically generate solutions with optimal QoS. \cite{gupta2015optimization} employs a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. \cite{yu2013adaptive} uses GP for finding near-optimal solutions that are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based representations, which are transformed from graph-based representations. \cite{da2015graphevol} introduces a promising graph-evolutionary approach to eliminate the transformation process. \cite{da2016particle} proposes an indirect PSO-based approach, where a service queue is used as an indirect representation that is decoded into a directed acyclic graph. However, these QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider the semantic matchmaking quality of service compositions.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. \cite{lecue2009optimizing} proposes a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic, which is associated to the resources of web services. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only evaluated with some simple cases.

@@

\section{Problem Description and Comprehensive Quality Model}\label{Motivation and Problem Description}\label{Motivation}\label{problemDes}\label{qualityModel}\label{Comprehensive_Quality_Model}\label{qualityModel}

@@

We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$. The inputs in $I_{S}$ and outputs in $O_{S}$ are parameters that are related to concepts in an ontology $\mathcal{O}$. The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively. These four QoS attributes are most commonly used \cite{zeng2003quality}.
% \textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received. \textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service. \textit{Reliability} ($r_S$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0. Similarly, \textit{availability} ($a_S$) is the probability that a service is accessible.

A \emph{service repository} $\mathcal{SR}$ is a finite collection of services with a common ontology $\mathcal{O}$. A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs. The inputs in $I_{T}$ and outputs in $O_{T}$ are parameters that are related to concepts in the ontology $\mathcal{O}$.

A service composition is commonly represented as a \emph{directed acyclic graph} (DAG). It nodes correspond to the services in the composition. Two services $S$ and $S'$ are connected by an edge $e$ if some output of $S$ serves as input for $S'$. Apparently, such outputs and inputs must semantically match to ensure the correct execution of the service composition. 
%Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
%To answer a request from a user a suitable service composition is sought. 
The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services. The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ is a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
%($a \perp b$)
In this paper we are only interested in robust compositions where only $exact$ and $plugin$ matches are considered, see \cite{lecue2009optimizing}. 
%
As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing. We suggest to consider the semantic similarity of concepts when comparing different $plugin$ matches. For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in Eq. (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively. 
\vspace{-0.2cm}

@@

\noindent with a suitable parameter $p, 0<p< 1$ to chosen, for discussion see Section \ref{PSO_based_approach}. However, if more than one pair of matched output and input exist from services $S$ and $S'$ respectively, $type_e$ and $sim_e$ will take on their average values.

@@

%\textbf{Definition 6.} Given $full match(a \Rightarrow b)$, $sm(a,b)$ is a function for measuring semantic matchmaking quality between two concepts, which returns a pair of values consisting of $type(a, b)$ and $q_{sim}(a, b)$ defined in Eq. (\ref{equation2}).

@@

%Since each $e$ defined in $E$ could have more than one $fullmatch(a \Rightarrow b)$ form a edge. Therefore, semantic matchmaking quality of one edge, denoted as $sm_e$ is defined in Eq. (\ref{equation3}), where $type_{e}$ and $sim_{e}$ are the average values of all involved $type(a, b)$ and $q_{sim}(a, b)$ respectively.

@@

%Consequently, in Eq. \ref{eqCQ}, the comprehensive quality $CQ$ consists of the aggregated semantic matchmaking quality $SM$ and the QoS calculation in DAG discussed before.
\vspace{-0.1cm}
\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria: 
\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{SIM} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent with $\sum_{k=1}^{6} w_k= 1$. We call this objective function the \emph{comprehensive quality model} for service composition.
The weights can be adjusted according to users' preferences. Herein, the individual criteria are normalised to a range between 0 to 1, where 1 means the best value and 0 means the worst. For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using Eq. (\ref{equation9}). To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$. $MT$ and $SIM$ have minimum value 0 and maximum value 1. The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for details see Section \ref{PSO_based_approach}.

@@

\noindent To solve the composition task best possible the goal is to find the maximum value of the objective function in Eq. (\ref{equation8}).

@@

\section{PSO-based Approach to Comprehensive Quality-Aware Automated Semantic Web Service Composition}\label{qswsc_approach}
\vspace{-0.8cm}
\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.4]{overview.pdf}}
 \caption{An overview of our PSO-based approach to comprehensive quality-aware automated semantic web service composition.}
 \label{overview}
\end{figure}
\vspace{-1.0cm}
\subsection{An Overview of our PSO-based Approach}\label{PSO_based_approach}

@@

Step 1: The composition process is triggered by a composition task, which is clearly defined in Section \ref{problemDes}.

Step 2: The composition task is used to discover all task-related service candidates using a greedy search algorithm adopted from \cite{ma2015hybrid}, which contributes to a shrunken service repository. This greedy search algorithm keeps adding outputs of the invoked services as available outputs (initialised with $I_{T}$) , and these available outputs are used to discover task-related services from a service repository and updated with the outputs of these discovered services. This operation is repeated until no service is satisfied by the available outputs. During the greedy search, an ontology-based cache ($cache$) is initialised, which stores the concept similarities of matched inputs and outputs of task-related candidates. This $cache$ is also used to discover services by checking whether $null$ is returned by given two output-related and input-related concepts.

Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes. In particular, these two differences are related to sorting a created service queue using service-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a $WG$ respectively. Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in Section \ref{POS-based_algomargin}.

\subsection{The Algorithms for our PSO-based Approach}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of a PSO-based web service composition technique (Algorithm \ref{novelSteps}) and a $WG$ creating technique from a service queue (Algorithm \ref{graph_building}). In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position. Each service candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0. In step 5, service candidates in the queue are sorted according to their corresponding weight values in descending order. In step 6, this sorted queue is used as one of the inputs of the forward decoding Algorithm \ref{graph_building} to create a $WG$. In step 7, the fitness value of the created $WG$ is the fitness value of the particle calculated by the comprehensive model discussed in Section \ref{Comprehensive_Quality_Model}.
\vspace{-0.5cm}
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particle in the swarm}{
     Create a service candidates queue and map service candidates to a particle's position vectors\;
     Sort the service queue by position vectors' weights\;
     Use Algorithm \ref{graph_building} to create a $WG$ from the service queue \;
     Calculate the $WG$ fitness value\;

@@

\vspace{-0.5cm}
Algorithm  \ref{graph_building} is a forward graph building algorithm extended from \cite{blum1997fast}. This algorithm takes one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}. Note that different service queues may lead to different $WGs$. In addition. $I_{T}$, $O_{T}$ and $cache$ are also taken as the inputs. Firstly, $Start$ and $End$ are added to $V$ of $WG$ as an initialisation, and $OutputSet$ is also created with $I_{T}$. The following steps are repeated until $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$. If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$. Otherwise, the second popped  $S$ from $queue$ is considered for these operations. Meanwhile, $e$ is created with $type_e$ and $sim_e$ if $S$ is added, and calculated using information provided from $cache$. This forward graph building technique could lead to more services and edges connected to the $WG$, these redundancies should be removed before $WG$ is returned.
\vspace{-0.5cm}

\begin{algorithm}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{createWeightedDAG}{createWeightedDAG}
 \SetKwProg{Procedure}{Procedure}{}{}
 %\LinesNumbered
 \SetNlSty{}{}{:}
 % \Procedure{}{
 \Input{ $I_T$, $O_T$, $queue$, $cache$}
 \Output{WG}
 $WG = (V, E)$\;
 $V \leftarrow$ \{$Start$, $End$ \} \;
 $OutputSet \leftarrow$ \{$I_{T}$\}\;
  \While { $O_{T}$ not satisfied by $OutputSet$}{
     \ForEach{$S$ in $queue$}{
      \uIf{$I_{S}$ satisfied by $OutputSet$}{  
        insert $S$ into $V$ \;  
        adjoin $O_{S}$ to $OutputSet$\;
        $queue$.remove $S$\;   
        $e \leftarrow$ calculate $type_e$, $sim_e$ using $cache$\;
        insert $e$ into $E$\;
       }	
     }
  }
 remove $dangling$ $nodes$ and $edges$ from $WG$\; 
 \KwRet $WG$\;
 %}
 \caption{Create a $WG$ from a sorted service queue.}
\label{graph_building}
\end{algorithm}

@@

\begin{figure}[h]
\centering{
\fbox{
\includegraphics[scale=.29]{comparisontest.pdf}}}
 \caption{An example for the comparison of the best solutions obtained based on the QoS model and on the comprehensive quality model for Task 3.}
 \label{comparisontest}
\end{figure}
\vspace{-1.0cm}
